### 2015-05-09 thesis/thesis/chap1/chap1.tex
rabeb comments

@@

\section{Proposal Organization}\label{sec:outline}
The rest of the proposal is organized as follows: We present in
Chapter 111 the background needed for our research along
with relevant related work. Chapter 222
provides the problem statement and presents our solution model in
two different scenarios with some preliminary results. Finally, in
Chapter 333, we present our conclusion,
future plan, and the timetable of our research.

@@

Within communities, services can exhibit competitive behavior as they provide the same functionalities and the number of users requests is finite.
However, for the same reason of being functionally similar, services can cooperate with each other, for example to substitute each other in order to perform some sub-tasks.
So as an extension of our work, we have proposed a framework in which services can opt for performing tasks if they feel they are capable enough
or decide to cooperate by showing the availability to perform some sub-tasks.
We have implemented an online learning mechanism for services with different capabilities to learn over time which strategy to choose based on their own and other services status and capabilities. After establishing states of our model and observing convincing results from our learning method, we plan to extend the learning process using reinforcement learning (Q-learning) techniques.

@@

\section{Report Organization}\label{sec:outline_s}
The rest of the report is organized as follows. We present in
Chapter 111 the background needed for our research along
with relevant related work. Chapter 222
provides the problem statement and presents our solution model in
two different scenarios with some preliminary results. Finally, in
Chapter 333, we present our conclusion,
future plan, and the timetable of our research.

>>>>

\emph{A research question about making architecture and decision making mechanism distributed}

\emph{A research question about adaptation and training needed for when agents have non-complete information}

@@

\section{Thesis Organization}\label{sec:outline}
The rest of the proposal is organized as follows: We present in
Chapter 111 the background needed for our research along
with relevant related work. Chapter 222
provides the problem statement and presents our solution model in
two different scenarios with some preliminary results. Finally, in
Chapter 333, we present our conclusion,
future plan, and the timetable of our research.

@@

Within communities, services can exhibit competitive behavior as they provide the same functionalities and the number of users requests is finite.
However, for the same reason of being functionally similar, services can cooperate with each other, for example to substitute each other in order to perform some sub-tasks.
So as an extension of our work, we have proposed a framework in which services can opt for performing tasks if they feel they are capable enough
or decide to cooperate by showing the availability to perform some sub-tasks.

%We have implemented an online learning mechanism for services with different capabilities to learn over time which strategy to choose based on their own and other services status and capabilities. After establishing states of our model and observing convincing results from our learning method, we plan to extend the learning process using reinforcement learning (Q-learning) techniques.

@@

\section{Thesis Organization}\label{sec:outline_s}
The rest of the thesis is organized as follows. We present in
Chapter 111 the background needed for our research along
with relevant related work. Chapter 222
provides the problem statement and presents our solution model in
two different scenarios with some preliminary results. Finally, in
Chapter 333, we present our conclusion,
future plan, and the timetable of our research.

### 2015-05-09 thesis/thesis/chap2/chap2.tex
rabeb comments

The idea of grouping web services within virtual structures was
fist proposed by Zeng et al. \cite{Zeng:2003:QDW:775152.775211}.
The authors defined web service community as collection of web
services providing the same functionality, but with different
quality metrics. Medjahed and Boubuettaya
\cite{journals/dpd/MedjahedB05} have proposed a framework and a
community builder mechanism which uses semantic analysis,
providing an ontological organization of web services having the
same domain of interest. The community builder would suggest web
services having similar operations to join the same community, or
form their own community in case the semantic analysis cannot find
any community that matches the service types.

@@

        In this direction, recently \cite{DBLP:conf/IEEEscc/LimTMB12,
        DBLP:conf/IEEEscc/KhosravifarABT11, 10.1109/TSC.2012.12} proposed mechanisms to help
        users and services maximize their gain. A two-player
        non-cooperative game between web services and community master was
        introduced in \cite{DBLP:conf/IEEEscc/KhosravifarABT11}. In this
        game-theoretic model, the strategies available to a web service
        when facing a new community are requesting to join the community,
        accepting the master's invitation to join the community, or
        refusing the invitation to join. The set of strategies for
        communities are inviting the web service or refusing the web
        service's join request. Based on their capacity, market share and
        reputation, the two players have different set of utilities over
        the strategy profiles of the game. The main limits of this game
        model are: 1) its consideration of only three quality parameters,
        while the other factors are simply ignored; and 2) the
        non-consideration of the web services already residing within the
        community. The game is only between the community master and the
        new web service, and the inputs from all the other members are
        simply ignored. The consideration of those inputs is a significant
        issue as existing web services can lose utility or payoff because
        of the new member, which can results in an unhealthy and unstable
        group. The problem comes from the fact that the existing members
        should collaborate with the new web services, so probably their
        performance as a group can suffer. Existing members may even
        deviate and try to join other communities if they are unsatisfied.
        Those considerations of forming stable and efficient coalitions
        are the main contributions of this research work.

@@

        In \cite{10.1109/TSC.2012.12}, a cooperative scheme among autonomous
        web services based on coalitional game theory has been introduced. The authors have proposed an algorithm to
        reach individually stable coalition partition for web services in order to
        maximize their efficiency. The communities choose new web services on the promise
        that it would benefit the community without decreasing any other web service's
        income. In their model, the worth of community is evaluated with high emphasis on
        availability metric and considering price and cost values only. The community structure is based on a coordination chain,
        where a web service is assigned as a \emph{primary} web service and the community task destribution
        method, will initially invoke the primary web service and only if the primary web service is unavailable
        will invoke the next backup web services as they are ordered in the coordination chain. However in cooperative models, it is preferred to
        have a real and active cooperative activity engaging all agents to perform the tasks more efficiently. Especially nowadays
        with recent advancement in cloud and hardware infrastructures availability is becoming less of an issue. So the backup web services
        in their model have a very low chance of getting jobs, especially the ones further in chain, which is huge waste of web services
        capabilities.

>>>>

In \cite{DBLP:journals/internet/BenatallahSD03}, Benatallah et al.
defined communities as \emph{Service Containers} that aggregate
substitutable web services providing a common functionality (same
set of operations). They abstracted \emph{Service Containers} as
web services that are created, advertised, discovered and invoked
just as elementary web services. The \emph{Container} is
considered as a manager that is responsible for web service
selection upon receiving a request on run-time. The authors have
proposed a scoring service based on non-functional requirements of
the request and web service capabilities to dynamically chose the
web service to perform the requested task. A similar concept was
proposed by Maamar et al. in
\cite{DBLP:journals/ijebr/MaamarSTBB09}. The authors introduced
web service communities as a collection of web services with a
common functionality but different QoS properties. A community
manager, upon receiving a request, delegates the request to one of
its current members. The choice is based on the performance
history and quality metrics of each web service. The authors have
proposed an efficient global web service selection algorithm in
order to approach quality constraints and preferences for
composite services which require aggregation of different types of
services to satisfy the user.

Benslimane et al. \cite{Liris-2770} have proposed a multi-layer
approach grouping similar Web services into communities and having
an interface implemented as an abstract web service for accessing
the community on top of the community layer. The interactions
between composite, management and community layers and the
bindings are performed by a generic driver called Open Software
Connectivity (OSC).

In \cite{managing-hela-jalel}, Limam and Akaichi have proposed web
service communities with centralized access across distributed web
services. They have proposed a framework for web service
management, query resolution among communities and a query caching
mechanism executed by the manager to improve the performance of
query resolution process among many distributed communities. The
key idea is to cache previous computed results for answering
future queries.

Maamar et al. initially in \cite{conf/webist/MaamarLBTS07} and
then comprehensively in \cite{DBLP:journals/ijebr/MaamarSTBB09}
proposed an architecture utilizing \emph{Contract-Net} protocol
for engineering task distribution within communities of web
services. The protocol is centrally executed by the community
manager. This architecture has been further developed in
\cite{CSTintercommunity, conf/IEEEscc/BenharrefSBB11,
conf/IEEEscc/KhosravifarBMMT10, conf/aina/LimTM11}. Two types of
roles have been distinguished for community members: masters and
slaves. Master web services and community managers that lead
communities and are responsible for membership management. They
can invite and convince slave web services to join the community,
and attract new slave web services to their communities by
awarding them better payoff. Moreover, they can eject some slave
members from the community to improve its overall reputation if
these members are misbehaving or cannot provide the promised QoS.

In \cite{Medjahed05adynamic}, Medjahed and Bouguettaya have
developed a community as a ``cluster'' that groups Web services
based on a specific area of interest. All web services in a given
community share the same functionality. These communities are
created by \emph{third party community providers} which use the
\emph{community ontology} as a template and define a set of
operations that all web services within a community should
provide. Using semantic analysis on web service operations, web
services either find and join a community with similar
functionality or create a new operation description for a new
community. The authors have described the concept of
\emph{community agents} associated to \emph{community providers}.
A community agent is responsible, among other things, of the
registration of services with the community. An example of a
community that provides health care services to senior citizens
has been used. In this example, a governmental entity is needed to
check the health care standards used by the members before
authorizing them to be part of the community. Such a central
entity is represented by the community agent. Thus, community
agents are playing the role of community managers. In a close work
\cite{Zeng:2003:QDW:775152.775211}, Zeng et al. have described a
global planning selection algorithm and a delegation algorithm to
be run when a request to execute an operation is received by the
community. This needs a central entity to run those algorithms.
Such entity plays the same role as the community coordinator or
manager.

@@

In this direction, recently \cite{DBLP:conf/IEEEscc/LimTMB12,
DBLP:conf/IEEEscc/KhosravifarABT11, 10.1109/TSC.2012.12} proposed
mechanisms to help users and services maximize their gain. A
two-player non-cooperative game between web services and community
master was introduced in
\cite{DBLP:conf/IEEEscc/KhosravifarABT11}. In this game-theoretic
model, the strategies available to a web service when facing a new
community are requesting to join the community, accepting the
master's invitation to join the community, or refusing the
invitation to join. The set of strategies for communities are
inviting the web service or refusing the web service's join
request. Based on their capacity, market share and reputation, the
two players have different sets of utilities over the strategy
profiles of the game. The main limits of this game model are: 1)
its consideration of only three quality parameters, while the
other factors are simply ignored; and 2) the non-consideration of
the web services already residing within the community. The game
is only between the community master and the new web service, and
the inputs from all the other members and their influence on the
master's decision are simply ignored. The consideration of those
inputs and this influence factor is a significant issue as
existing web services can lose utility or payoff because of the
new member, which can result in an unhealthy and unstable group.
The problem comes from the fact that the existing members should
collaborate with the new web services, so probably their
performance as a group can suffer. Existing members may even
deviate and try to join other communities if they are unsatisfied.
Those considerations of forming stable and efficient coalitions
are the main contributions of our paper.

@@

In \cite{10.1109/TSC.2012.12}, a cooperative scheme among
autonomous web services based on coalitional game theory has been
introduced. The authors have proposed an interesting algorithm to
reach individually stable coalition partition for web services in
order to maximize their efficiency. The communities choose new web
services on the promise that it would benefit the community
without decreasing any other web service's income. In the proposed
model, the worth of community is evaluated with high emphasis on
the availability metric and considering price and cost values
only. The community structure is based on a coordination chain,
where a web service is considered as a \emph{primary} web service
and the community task-distribution method initially invokes the
primary web service and only if the primary web service is
unavailable, the method invokes the next backup web services as
they are ordered in the coordination chain. We believe that this
coordination chain limits the cooperation power as it introduces a
sort of hierarchy. However, in pure and open cooperative models,
such as the one we propose in this paper, active cooperation
activities engaging simultaneously many agents so that they can
perform the tasks more efficiently are being used. Moreover, if
the availability is high, which is the case nowadays with the
recent advancements in cloud and hardware infrastructures, the
backup web services will end-up having a very low chance of
getting jobs, especially the ones further in the chain. This will
results in a considerable waste of web services capabilities.

%All the proposed frameworks share a common aspect, which is providing the solution based on assumption of having complete information of all services and performing evaluations based on a large number of input each time they want to adopt a strategic decision making process.
%So basically These solutions generally suffer from high complexity, which makes decision making impossible in an on-demand fashion, or they simplify important aspects to make it practical in the real world, thereby hurting the decision making performance. We address this issue by introducing DDM a framework that operates based on a trained model that regulates web service agents' decision making process in terms of cooperating with one another. After being trained, web services get to compute expectations as utilities they would gain while cooperating with communities of different characteristics. Therefore web services and communities can make prudent decisions when inviting a web service to join or accepting a join inquiry initiated from a web service. In general, DDM equips web services with efficient methods for foreseeing how their choices will impact their long-term and short-term goals; therefore, opting for best decision available.
